Developing a preprint culture in biology

### 2012-10-05 ms.tex
One more minor editorial change to Biological Sciences section
Minor edits to the arXiv section

Another major concern is that if a researcher posts a public preprint that they
will not be allowed to submit their paper to their journal of choice. This is 
based on a certain interpretation
of the Ingelfinger rule: scientists should not publish the same manuscript twice
\cite{alt96}. However, preprints are not peer-reviewed papers and posting to a
public server does not constitute publication in a peer-reviewed journal.
A preprint is simply a document that allows ideas to spread and be discussed, 
but it is not yet formally validated by the peer-review system. This is why the
majority of publishers do not see arXiv and similar services as a violation of the
Ingelfinger rule. Almost all of the major publishers in biology are preprint-friendly,
including: Nature Publishing Group, PLOS, BMC, PNAS, Science (mostly) \ref{table:policies},
and all the journals from Elsevier %something is off in the formatting here
and Springer.  The Ecological Society of America and the Genetics Society of
America also recently changed their policies to allow public preprints.  Few
scientific publications will not consider a manuscript submitted to a public
preprint server. In fact, \emph{Nature} responded to the rumour that they refused
manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
stand in the way of communication between researchers. We seek rather to add
value for authors and the community at large in our peer review, selection and
editing'' \cite{nat05}. Still, a few journals adopt a ``by default'' hostile attitude
towards preprints, mostly due to the lack of clear policy of the publishers, or
perhaps because a preprint culture has not developed in biology and the practice
is still considered unusual. As an example, Wiley-Blackwell, which publishes
some leading journals, has no official policy on the matter.

@@

Authors must either have their arXiv submission available under an open license
or grant arXiv a non-exclusive and irrevocable license to distribute the work.
In either case, arXiv does not require copyright transfer and only requires the
rights to distribute submitted articles in perpetuity. Thus, submitting to arXiv
does not in itself prevent the authors from transferring their rights to a
publisher, which is why most publishers tolerate arXiv, even though they ask the
authors to transfer their right to them upon acceptance of the article.

Most papers posted to arXiv are eventually printed in journals but there are
notable exceptions, such as Perelman's landmark paper leading to the proof of
the Poincar\'{e} conjecture \cite{2002math.....11159P}.  However, arXiv has
never sought to replace scientific journals and explicitly states that it serves
a different function as ``an openly accessible, moderated repository for
scholarly articles in specific scientific disciplines.'' arXiv is now
administered by the Cornell University Libraries, with funding coming from
voluntary pledges by academic institutions along with matching funds from the
Simons Foundation \cite{arxiv_future}.  One-hundred twenty six of the top
two-hundred institutions in terms of downloads have provided the operating
budget for arXiv over the next five years.  This plan reduces the financial
burden on Cornell University and transfers governance to a collaborative
community in accordance with arXiv's key principles.  arXiv takes numerous
measures to ensure that the repository will remain permanently available and
submissions will be readable.

>>>>

Another major concern is that if a researcher posts a public preprint that they
will not be allowed to submit their paper to their journal of choice. This is 
based on a certain interpretation
of the Ingelfinger rule: scientists should not publish the same manuscript twice
\cite{alt96}. However, preprints are not peer-reviewed papers and posting to a
public server does not constitute publication in a peer-reviewed journal.
A preprint is simply a document that allows ideas to spread and be discussed, 
but it is not yet formally validated by the peer-review system. This is why the
majority of publishers do not see arXiv and similar services as a violation of the
Ingelfinger rule. Almost all of the major publishers in biology are preprint-friendly,
including: Nature Publishing Group, PLOS, BMC, PNAS, Science (mostly) \ref{table:policies},
and all the journals from Elsevier %something is off in the formatting here
and Springer.  The Ecological Society of America and the Genetics Society of
America also recently changed their policies to allow public preprints.  Few
scientific publications will not consider a manuscript submitted to a public
preprint server. In fact, \emph{Nature} responded to the rumour that they refused
manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
stand in the way of communication between researchers. We seek rather to add
value for authors and the community at large in our peer review, selection and
editing'' \cite{nat05}. Still, a few journals adopt a ``by default'' hostile attitude
towards preprints, mostly due to the lack of clear policy of the publishers, or
perhaps because a preprint culture has not developed in biology and the practice
is still considered unusual. As an example, Wiley-Blackwell, which publishes
some of the leading journals in biology, has no official policy on the matter.

@@

Authors must either have their arXiv submission available under an open license
or grant arXiv a non-exclusive and irrevocable license to distribute the work.
In either case, arXiv does not require copyright transfer and only requires the
rights to distribute submitted articles in perpetuity. Thus, submitting to arXiv
does not prevent the authors from transferring their rights to a
publisher.

Most papers posted to arXiv are eventually printed in journals but there are
notable exceptions including Perelman's landmark paper leading to the proof of
the Poincar\'{e} conjecture \cite{2002math.....11159P}.  However, arXiv has
never sought to replace scientific journals and explicitly states that it serves
a different function as ``an openly accessible, moderated repository for
scholarly articles in specific scientific disciplines.'' arXiv is now
administered by the Cornell University Libraries, with funding coming from
voluntary pledges by academic institutions along with matching funds from the
Simons Foundation \cite{arxiv_future}.  One-hundred twenty six of the top
two-hundred institutions in terms of downloads have provided the operating
budget for arXiv over the next five years.  This plan reduces the financial
burden on Cornell University and transfers governance to a collaborative
community in accordance with arXiv's key principles.  arXiv takes numerous
measures to ensure that the repository will remain permanently available and
submissions will be readable.
